Using UPRN to determine household composition

### 2021-04-16 using_UPRN_to_determine_household_structure.Rmd
Cleaned up UPRN proof of concept script

library(tidyverse)
```

@@

# possible_dates_character <- 
#   as.character(
#     seq.Date(
#       from = as.Date("2015-01-01"),  # TODO: complete this, and then sample from the vector instead, possibly character to make it less intense!
#       to = as.Date("2020-12-31"),
#       by = "days"
#     ))

@@

fake_chi <- 
  tibble(
    id_chi = 1:n_individuals,  # integer id
    n_rows = round(runif(n = n_individuals, min = min_records, max = max_records))  # a random number of records for each id, these are "uncounted" in the next step
    ) %>%
  uncount(weights = n_rows) %>%  # create N entries for each id based on above random N
  mutate(
    uprn_chi = sample(x = 1:n_addresses, size = nrow(.), replace = TRUE),  # sample addresses with replacement
    date_address_change = as.Date(x = rdunif(n = nrow(.),  # random dates
                                 a = as.integer(as.Date("2015-01-01")),
                                 b = as.integer(as.Date("2020-12-31"))),
                      origin = "1970-01-01")
    ) %>%
  arrange(id_chi, date_address_change) %>%
  group_by(id_chi) %>%
  mutate(episode_id = 1:n()) %>%
  ungroup

@@

number_of_household_members <-
  household_members %>%
  group_by(id_death) %>%
  summarise(num_household_members = n_distinct(id_chi), .groups = "drop") %>%
  tidyr::complete(id_death = fake_deaths$id_death, fill = list(num_household_members = 0))

# chis_with_matching_uprn_episodic <- 
#   chi_with_matching_uprn %>%
#   select(id_chi, episode_id) %>%
#   mutate(next_episode_id = episode_id + 1) %>%
#   left_join(fake_chi, by = c("id_chi", "next_episode_id"="episode_id")) %>%
#   mutate(date_episode_end = replace_na(date_address_change, replace = ymd("2021-01-01")))
#

>>>>

library(tidyverse)
library(lubridate)  # for working with dates
```

@@

possible_dates_character <-  # I thought that keeping dates as character vector until I need to compute with them would speed things up, but it's okay actually
  as.character(
    seq.Date(
      from = as.Date("2015-01-01"),  # TODO: complete this, and then sample from the vector instead, possibly character to make it less intense!
      to = as.Date("2020-12-31"),
      by = "days"
    ))

@@

# fake_deaths %>% ggplot(aes(x=date_death)) + geom_bar()

fake_chi <- 
  tibble(
    id_chi = 1:n_individuals,  # integer id
    n_rows = round(runif(n = n_individuals, min = min_records, max = max_records))  # a random number of records for each id, these are "uncounted" in the next step
    ) %>%
  uncount(weights = n_rows) %>%  # create N entries for each id based on above random N
  mutate(
    uprn_chi = sample(x = 1:n_addresses, size = nrow(.), replace = TRUE),  # sample addresses with replacement
    date_address_change = as.Date(x = rdunif(n = nrow(.),  # random dates
                                 a = as.integer(as.Date("2015-01-01")),
                                 b = as.integer(as.Date("2020-12-31"))),
                      origin = "1970-01-01")
    ) %>%
  arrange(id_chi, date_address_change)

@@

number_of_household_members <-
  household_members %>%
  group_by(id_death) %>%
  summarise(num_household_members = n_distinct(id_chi), .groups = "drop") %>%
  tidyr::complete(id_death = fake_deaths$id_death, fill = list(num_household_members = 0))  # add records of individuals with no household members

number_of_household_members %>% ggplot(aes(x=num_household_members)) + geom_bar() + theme_minimal()
```
